\documentclass[11pt]{article}

\usepackage[left=0.75in,right=0.75in,top=0.6in,bottom=0.6in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
\setlength{\emergencystretch}{2em}
\setlist[itemize]{leftmargin=*, topsep=2pt, itemsep=1.5pt, parsep=0pt, partopsep=0pt}

\titleformat{\section}
  {\large\bfseries}
  {}{0pt}{}
  [\vspace{-2pt}\titlerule]
\titlespacing*{\section}{0pt}{7pt}{4pt}

\newcommand{\role}[4]{%
  \textbf{#1} \hfill #2\\
  \textit{#3} \hfill \textit{#4}
}

\begin{document}

{\LARGE\textbf{Achraf Boutzad}}\\[-1pt]
{\large\textbf{Software Engineer $|$ DevOps Engineer}}\\[-1pt]
Marrakech, Morocco $|$ +212 695 143 629 $|$ \href{mailto:achrafboutzad@gmail.com}{achrafboutzad@gmail.com} $|$ \href{https://www.linkedin.com/in/achraf-boutzad/}{LinkedIn} $|$ \href{https://achrafboutzad.com}{achrafboutzad.com}

\section{Professional Summary}
Software Engineer and DevOps Engineer with one year of experience delivering operational software for MARWA through Haldorix. Builds real-time dashboards, monitoring systems, APIs, and IoT integrations using Spring Boot, FastAPI, Next.js, Kafka, MQTT, WebSockets, and CI/CD.

\section{Core Competencies}
\begin{itemize}
  \item \textbf{Methodologies:} Agile, Scrum, SDLC, iterative delivery, continuous improvement, DevOps practices
  \item \textbf{Analysis \& Design:} Requirements analysis, UML, Merise, microservices, event-driven architecture, REST API design, data modeling
  \item \textbf{Testing \& QA:} JUnit, Selenium, SonarQube, unit testing, integration testing, API testing, code quality review
  \item \textbf{Collaboration \& Documentation:} Cross-functional teamwork, technical documentation, stakeholder communication, ClickUp, customer orientation
  \item \textbf{Technical Skills:} Java/JEE, Spring Boot, Python, FastAPI, JavaScript, TypeScript, Next.js, React, Angular, SQL/PLSQL, HTML, CSS, Tailwind CSS
  \item \textbf{Tools \& Platforms:} Git, GitHub, CI/CD, Docker, Linux, Kafka, MQTT, WebSockets, MySQL, Oracle, SQL Server, Power BI, Streamlit
\end{itemize}

\section{Professional Experience}
\role{Software Engineer}{2025--Present}{Haldorix -- MARWA Corporation}{Morocco}
\begin{itemize}
  \item Engineered real-time production dashboards and operational monitoring features that increased workflow visibility and contributed to an estimated 50\% improvement in team productivity.
  \item Optimized order and station workflows by exposing bottlenecks, queue status, and processing KPIs, helping reduce operational waiting time by approximately 30\%.
  \item Integrated backend services, WebSocket-based updates, and event-driven data flows to deliver timely production metrics and improve responsiveness for operational users.
  \item Automated build, testing, and deployment activities through Git-based CI/CD practices, shortening release preparation and reducing deployment-related defects.
  \item Collaborated with MARWA stakeholders and Haldorix engineers to translate business requirements into maintainable features, document changes, and support reliable releases.
\end{itemize}

\role{Business Intelligence Intern}{May 2023--Jul 2023}{Faculty of Sciences Semlalia}{Marrakech, Morocco}
\begin{itemize}
  \item Designed and implemented a decision-support information system for road-safety data analysis.
  \item Integrated road-safety datasets into a centralized data warehouse, improving analytical consistency and accessibility.
  \item Built multidimensional analyses using OLAP cubes and MDX queries to accelerate structured exploration of operational indicators.
  \item Developed interactive Power BI dashboards for near-real-time visualization and clearer reporting of key metrics.
\end{itemize}

\section{Projects \& Analytics Experience}
\textbf{Real-Time Production Monitoring and Bottleneck Analytics Platform} -- Next.js, Spring Boot, WebSockets, Kafka, MySQL
\begin{itemize}
  \item Architected a live operations platform that streams station status, order progress, queue depth, throughput, waiting time, and efficiency KPIs to responsive dashboards.
  \item Implemented event-driven processing, WebSocket updates, alert rules, historical trend analysis, and role-based views for production supervision and bottleneck detection.
\end{itemize}

\textbf{Industrial IoT Telemetry and Alerting System} -- FastAPI, Python, MQTT, Kafka, PostgreSQL, Docker
\begin{itemize}
  \item Built an IoT ingestion layer for device telemetry using MQTT, asynchronous FastAPI services, validation pipelines, and Kafka-based event distribution.
  \item Added threshold alerts, device-health monitoring, time-series aggregation, retry handling, and containerized deployment for resilient industrial integrations.
\end{itemize}

\textbf{Distributed Service Monitoring and Incident Platform} -- Spring Boot, Kafka, WebSockets, SQL, Docker
\begin{itemize}
  \item Developed microservices that collect application health, job status, error events, and deployment signals and expose them through real-time monitoring APIs.
  \item Designed service-level dashboards, incident timelines, audit logs, and notification workflows to support observability and faster root-cause analysis.
\end{itemize}

\textbf{Workflow and Order Orchestration System} -- FastAPI, Next.js, WebSockets, MySQL
\begin{itemize}
  \item Implemented configurable workflows, order-state transitions, assignment rules, SLA timers, live status synchronization, and analytics for operational decision-making.
\end{itemize}

\section{Education}
\textbf{Specialized Master's in Information Systems Engineering} \hfill 2023--2025\\
Faculty of Sciences Semlalia, Marrakech

\textbf{Bachelor's Degree in Mathematics and Computer Science} \hfill 2018--2023\\
Faculty of Sciences Semlalia, Marrakech

\textbf{Baccalaureate in Mathematical Sciences A} \hfill 2017--2018\\
Lycee Akensouse, Essaouira

\section{Certifications}
\begin{itemize}
  \item Engineering Practices for Building Quality Software -- Coursera
  \item Machine Learning with Python -- Coursera
\end{itemize}

\end{document}
